\documentclass[10pt, letterpaper]{article}

% Packages:
\usepackage[
    ignoreheadfoot, % set margins without considering header and footer
    top=1.1 cm, % seperation between body and page edge from the top
    bottom= 1 cm, % seperation between body and page edge from the bottom
    left=2 cm, % seperation between body and page edge from the left
    right=2 cm, % seperation between body and page edge from the right
    footskip=1.0 cm, % seperation between body and footer
    % showframe % for debugging 
]{geometry} % for adjusting page geometry
\usepackage[explicit]{titlesec} % for customizing section titles
\usepackage{tabularx} % for making tables with fixed width columns
\usepackage{array} % tabularx requires this
\usepackage[dvipsnames]{xcolor} % for coloring text
\definecolor{primaryColor}{RGB}{0, 79, 144} % define primary color
\usepackage{enumitem} % for customizing lists
\usepackage{fontawesome5} % for using icons
\usepackage{amsmath} % for math
\usepackage[
    pdftitle={Rayane GETA's Resume},
    pdfauthor={Rayane GETA},
    pdfcreator={LaTeX with RenderCV},
    colorlinks=true,
    urlcolor=primaryColor
]{hyperref} % for links, metadata and bookmarks
\usepackage[pscoord]{eso-pic} % for floating text on the page
\usepackage{calc} % for calculating lengths
\usepackage{bookmark} % for bookmarks
\usepackage{lastpage} % for getting the total number of pages
\usepackage{changepage} % for one column entries (adjustwidth environment)
\usepackage{paracol} % for two and three column entries
\usepackage{ifthen} % for conditional statements
\usepackage{needspace} % for avoiding page brake right after the section title
\usepackage{iftex} % check if engine is pdflatex, xetex or luatex

% Ensure that generate pdf is machine readable/ATS parsable:
\ifPDFTeX
    \input{glyphtounicode}
    \pdfgentounicode=1
    \usepackage[T1]{fontenc}
    \usepackage[utf8]{inputenc}
    \usepackage{lmodern}
\fi

\usepackage[default, type1]{sourcesanspro} 
\usepackage{fontawesome5}

% Some settings:
\AtBeginEnvironment{adjustwidth}{\partopsep0pt} % remove space before adjustwidth environment
\pagestyle{empty} % no header or footer
\setcounter{secnumdepth}{0} % no section numbering
\setlength{\parindent}{0pt} % no indentation
\setlength{\topskip}{0pt} % no top skip
\setlength{\columnsep}{0.15cm} % set column seperation
\makeatletter
\let\ps@customFooterStyle\ps@plain % Copy the plain style to customFooterStyle
\patchcmd{\ps@customFooterStyle}{\thepage}{
    \color{gray}\textit{\small }
}{}{} % replace number by desired string
\makeatother
\pagestyle{customFooterStyle}

\titleformat{\section}{
    % avoid page breaking right after the section title
    \needspace{4\baselineskip}
    % make the font size of the section title large and color it with the primary color
    \Large\color{primaryColor}
}{
}{
}{
    % print bold title, give 0.15 cm space and draw a line of 0.8 pt thickness
    % from the end of the title to the end of the body
    \textbf{#1}\hspace{0.15cm}\titlerule[0.8pt]\hspace{-0.1cm}
}[] % section title formatting

\titlespacing{\section}{
    % left space:
    -1pt
}{
    % top space:
    0.3 cm
}{
    % bottom space:
    0.2 cm
} % section title spacing

% Custom bullet points
\newenvironment{highlights}{
    \begin{itemize}[
        topsep=0.10 cm,
        parsep=0.10 cm,
        partopsep=0pt,
        itemsep=0pt,
        leftmargin=0.4 cm + 10pt
    ]
}{
    \end{itemize}
}

\newenvironment{onecolentry}{
    \begin{adjustwidth}{
        0.2 cm + 0.00001 cm
    }{
        0.2 cm + 0.00001 cm
    }
}{
    \end{adjustwidth}
}

\newenvironment{twocolentry}[2][]{
    \onecolentry
    \def\secondColumn{#2}
    \setcolumnwidth{\fill, 4.5 cm}
    \begin{paracol}{2}
}{
    \switchcolumn \raggedleft \secondColumn
    \end{paracol}
    \endonecolentry
}

\newenvironment{twocolentrysame}[2][]{
    \onecolentry
    \def\secondColumn{#2}
    \setcolumnwidth{\fill, 8cm}
    \begin{paracol}{2}
}{
    \switchcolumn \raggedleft \secondColumn
    \end{paracol}
    \endonecolentry
}

% Header format
\newenvironment{header}{
    \setlength{\topsep}{0pt}\par\kern\topsep\centering\color{primaryColor}\linespread{1.5}
}{
    \par\kern\topsep
}



% Begin Document
\begin{document}
    \newcommand{\AND}{\unskip
        \cleaders\copy\ANDbox\hskip\wd\ANDbox
        \ignorespaces
    }
    \newsavebox{\ANDbox}\savebox\ANDbox{}
    
    \placelastupdatedtext
    \begin{header}
        \fontsize{22 pt}{22 pt}
        \textbf{Double-degree Mechatronics and AI Engineer}\\
        \vspace{0.3 cm}
        \fontsize{15 pt}{15 pt}
        \textbf{Rayane GETA --- Seeking a robotics/IA engineer position}
        \vspace{0.3 cm}

        \normalsize
        \mbox{{\footnotesize\faMapMarker*}\hspace*{0.1cm}Open to relocation}%
        \kern 0.25 cm%
        \AND%
        \kern 0.25 cm%
        \mbox{\hrefWithoutArrow{{\footnotesize\faEnvelope[regular]}\hspace*{0.13cm}rayane.geta@gmail.com}}%
        \kern 0.25 cm%
        \AND%
        \kern 0.25 cm%
        \mbox{\hrefWithoutArrow{{\footnotesize\faPhone*}\hspace*{0.13cm}+33763570092}}%
        \kern 0.25 cm%
        \AND%
        \kern 0.25 cm%
        \mbox{\href{https://www.linkedin.com/in/rayane-geta}{\normalsize\faLinkedin\hspace*{0.13cm}rayane-geta}}%
        \kern 0.25 cm%
        \AND%
        \kern 0.25 cm%
        \mbox{\href{https://rayane-maker.github.io}{\normalsize\faGlobeAmericas\hspace*{0.13cm}rayane-maker.github.io}}%

    \end{header}

    \vspace{0.2 cm - 0.2 cm}



    
 \section{Education}
    \begin{twocolentry}{
        Brest, France \newline
        September 2023 - 2025
    }
        \textbf{ENSTA (National Institute of Advanced Technologies)}, Master of Science
        \begin{highlights}
            \item \textbf{Relevant Coursework:} Computer Vision, Radar and Remote Sensing, Software Engineering, Machine Learning, Linear and Nonlinear Optimization\\
        \end{highlights}
    \end{twocolentry}

    \vspace{0.1cm}

    \begin{twocolentry}{
        Limoges, France \newline
        September 2021 - 2025
    }
        \textbf{ENSIL-ENSCI (National Graduate Engineering School of Limoges)}, Master of Science
        \begin{highlights}
            \item \textbf{Relevant Coursework:} Control Systems, %Powertrain Engineering,% 
            Robotics, Mechanical Design.
        \end{highlights}
    \end{twocolentry}



 \section{Professional Experience}


\begin{twocolentry}{
        Barcelona, Spain \newline
        May 2025 – Nov. 2025
    }
        \textbf{Institut de Robòtica i Informàtica Industrial (IRI)}, Robotics and AI Engineer Intern
        \begin{highlights}
            \item Extended an assistive robotic feeding system to handle diverse unseen food types using ROS1 and BehaviorTree.CPP.
            \item Built a semi-automated food manipulation sandbox enabling simultaneous demonstration learning and systematic dataset generation.
            \item Designed embedded vision pipelines for food segmentation, texture classification plate detection, and overflow analysis leveraging classical computer vision and CNN (design and training).
            \item Implemented custom collision detection/response system enabling safe collaborative robot behavior and touch sensing.\\
        \end{highlights}
    \end{twocolentry}


    \begin{twocolentry}{
        Bordeaux, France \newline
        April 2024 – Aug. 2024
    }
        \textbf{Aerix Systems}, Embedded System and AI Engineer Intern
        \begin{highlights}
            \item Developed monocular visual odometry for an omnidirectional drone in C++.
            \item Designed multi-threaded real-time odometry software architecture.
            \item Integrated a deep-neural network for 3D vision and odometry enhancement.
            \item Documented the software with Doxygen.\\
            %\item Applied SOLID design principles to build high-quality, modular software solution.\\%
        \end{highlights}
    \end{twocolentry}
    

    \begin{twocolentry}{
        Albi, France \newline
        May 2023 – Aug. 2023
    }
        \textbf{CRITT Automatisation \& Robotique}, Mechatronic Engineer Intern
        \begin{highlights}
            \item Designed, machined and assembled mechanical parts for industrial machines.
            \item Developed HMI software and programmed PLCs using Siemens TIA Portal.
        \end{highlights}
    \end{twocolentry}

    



    \section{Academic and Personal Projects}
    
%    \begin{onecolentry}
%    \textbf{National Student Entrepreneur (SNEE)}
%     \begin{highlights}
%        \item Developing an application catering to dancers and choreographers’ needs.
%        \item Recognized by Pepite Bretagne for my entrepreneurial initiative.
%        \item Gained access to resources, mentoring, and networks to support project development.\\
%     \end{highlights}
%     \end{onecolentry}

    % \begin{onecolentry}
    % \textbf{Pan-Tilt Tracker - Personal project}
    % \begin{highlights}
    %     \item Created a motorized smartphone holder with auto-tracking for capturing my dance sessions.
    %     \item Developed the Android app for video capture and tracking. Designed and assembled 3D-printed parts.\\
    % \end{highlights}
    % \end{onecolentry}

    \begin{onecolentry}
        \textbf{Multicam - School group project}
        \begin{highlights}
            \item Supervised development of a multi-camera (ESP32-Cam) system for multi-people safety monitoring using YOLOv8.
            \item Implemented custom voting based multi-person tracker robust to occlusions.
        \end{highlights}
    \end{onecolentry}

    % \begin{onecolentry}
    %     \textbf{Vehicle simulator game}
    %     \begin{highlights}
    %         \item Developed a vehicle simulator game using Unity, with custom drivetrain and wheel physics simulations.
    %         \item Implemented classic AI algorithms for virtual opponents, leveraging geometry-based methods.\\

    %     \end{highlights}
    % \end{onecolentry}


    \textbf{More projects spanning robotics, AI, and software development in my portfolio: \href{https://rayane-maker.github.io}{
    %\normalsize\faGlobeAmericas\hspace*{0.13cm}
    rayane-maker.github.io}}%   



    
    \section{Skills}
    \begin{twocolentrysame}{
        \textbf{DevOps} Git, Docker, Google Colab\\
        \textbf{Languages} English, French, Spanish.\\
        \textbf{Soft Skills} Teamwork, Self-Learning, Critical Thinking, Problem Solving, Communication Skills.
        }
        
        \textbf{Coding Languages} C/C++, JAVA, Python, Javascript, Matlab\\      
        \textbf{Frameworks} ROS, BehaviorTree.CPP, Pytorch, Tensorflow\\       
        \textbf{Control System} Matlab, Simulink, Amesim, CoppeliaSim\\
        \textbf{Mechanical Design} Solidworks, 3DExperience, Catia      

    \end{twocolentrysame}



    
    \section{Hobbies and Activities}
\begin{onecolentry}{\begin{highlights}
        \item Hip Hop Dance (2015 - Present, Public performances, {Styles} : Animation, Popping, Krump)
        \item Shell Eco-marathon (2022, Main Pilot, {Location}: Assen, Netherlands)
        % \item Weight Training (2022 - Present)
        \end{highlights}}
        
\end{onecolentry}


\end{document}
